Standalone Tactics using OpenTheory

### 2011-10-14 paper.tex
first stab at abstract

\begin{abstract}
\end{abstract}

>>>>

\begin{abstract}
Tactics, functions that compute low-level inferences to achieve a high-level reasoning goal, are usually developed within and tied to a particular proof assistant, which leads to code duplication across different systems and inhibits reuse.
As formal methods are applied to larger problems, projects spanning multiple proof assistants benefit more from interoperability and access to the union of all implemented tactics.
Using the OpenTheory proof exchange format, we show how to turn a tactic implemented for one system into one available to many via the web.
This enables, for example, LCF-style proof reconstruction efforts for fast automatic provers to be shared by users of multiple proof assistants and removes the need for each user to install the automatic prover.
\end{abstract}
